Kernel Smoothing And Heat Equation

### 2020-12-01 latex/draft.tex
update latex and code for debugging the extreme boundary point

The boundary behavior of the adaptive scenario is not ideal. We then modified $\texttt{max.window}$ from $\texttt{xrange/5}$ to $\texttt{xrange/0.1}$. The situation gets better.

@@

>>>>

Although the adaptive bandwidth smoother perform well in general, but the boundary behavior of the adaptive bandwidth smoother is not ideal. We then modified $\texttt{max.window}$ from $\texttt{xrange/5}$ to $\texttt{xrange/0.1}$. The situation gets better.

@@

Now we compare the empirical MSE with the theoretical MSE on the extreme point at the boundary.

\textit{Flash back:}
$$\text{MSE}_j=  \frac{\sigma^2}{2\sqrt{\pi \cdot b}}  + \left[\frac{\partial^2 u}{2\partial x^2}\cdot b \right]^2$$

\begin{table}[H]
\centering
\begin{tabular}{l|l| l}
\hline\hline
& (theoretical MSE =$1.96\times 10^{-7}$) & (theoretical MSE =$3.95\times 10^{-7}$)\\
k & empirical MSE  ($\sigma=1$) &empirical MSE  ($\sigma=0.1$) \\\hline 
0.1&0.0019 $(8.15\times 10^{-6})$ & 0.0021 $(7.59\times 10^{-6})$\\
1 & 0.0020 $(7.80\times 10^{-6})$ &0.0019 $(6.76\times 10^{-6})$\\
2 & 0.0020 $(8.09\times 10^{-6})$ &0.0019 $(7.09\times 10^{-6})$\\
2.1 & 0.4448 $(0.0072)$ &0.4408 (0.0071)\\
3 & 0.5124 $(0.0128)$ & 0.5220 (0.0123)\\
4 & 0.4107 $(0.0122)$ & 0.4070 (0.0131)\\
5 & 0.3116 $(0.0124)$ & 0.3147 (0.0136)\\\hline
\end{tabular}
\caption{1000 times simulation for empirical MSE at extreme point at boundary}
\end{table}

\begin{figure}[H]
\includegraphics[width=\linewidth]{pic/sim.plot6.eps}
\includegraphics[width=\linewidth]{pic/sim.plot7.eps}
\includegraphics[width=\linewidth]{pic/sim.plot8.eps}
\includegraphics[width=\linewidth]{pic/sim.plot9.eps}
\end{figure}
